We need a way to reduce the set of solutions and consequently the huge search space from the symmetries. A general approach is to impose an \textbf{ordering}
between the decision variables to avoid the permutations, in particular:
$$ X_1 \leq X_2 \leq \dots \leq X_n \text{ when } [X_1, X_2, \dots, X_n] \text{ are all symmetric.} $$
Notice, at least one solution from each set of symmetrically equivalent solutions must remain.
\begin{example}[title = Improved model]
    \textbf{Symmetry breaking constraints}.
    \begin{itemize}
        \renewcommand{\labelitemi}{-}
        \item $X_1 < X_2 < \dots < X_m$
        \item $X_1 = 0$
        \item $D_{12} < D_{(m-1)m}$
    \end{itemize} \vspace{7pt}
    Notice: symmetry breaking constraints and implied constraints are not the same thing. An implied constraint is a logical implication that does not change the solution at all, while a symmetry breaking constraint is not a logical implication, having it inside our model could change the state of the solution. \vspace{7pt}

    \textbf{New objective}. 
    \begin{itemize}
        \renewcommand{\labelitemi}{-}
        \item $\textit{minimize}(X_m)$
    \end{itemize}
\end{example}
At first sight, any global constraint seems to be a good constraint for our solver, like $\textit{alldifferent}(\dots)$ constraint. However, after we 
introduced these symmetry breaking constraints, the $\textit{alldifferent}(\dots)$ constraint is not useful anymore, it becomes \textbf{semantically} and \textbf{computationally
redundant}. Symmetry breaking constraints enable \textbf{constraint semplification}.
\begin{example}[title = Simplified improved model]
    \textbf{Symmetry breaking constraints}.
    \begin{itemize}
        \renewcommand{\labelitemi}{-}
        \item $X_1 < X_2 < \dots < X_m$ \\ $\textit{alldifferent}([X_1, X_2, \dots, X_m])$ constraint becomes redundant. In the process of remodelling, delete $\textit{alldifferent}([X_1, X_2, \dots, X_m])$ constraint can be a good idea to avoid redundancy. In addition, also the first constraint introduced in the previous section ($\textit{for all } i < j, \textit{ } D_{ij} = |X_i - X_j|$) can be simplified as follows:
        \begin{itemize}
            \renewcommand{\labelitemi}{-}
            \item $\text{for all } i < j, \text{ } D_{ij} = X_i - X_j$
        \end{itemize}
        We don't need anymore absolute values, exploiting the decision variables order imposed by symmetry breaking constraints.
    \end{itemize} \vspace{7pt}
\end{example}